### 2014-02-28 paper/monad.tex
Drop the cite.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Monads were originally proposed as a method for organizing computational
effects~\cite{Moggi:1991:NCM:116981.116984}.  One of the key questions
of interest was how to modularly build more complex computational
effects out of simpler ones.  One particular approach, the
\emph{incremental
approach}~\cite{Benton00monadsand,Liang95monadtransformers}, utilizes
monad transformers, which add an extra computation feature to a
pre-existing monad.  In the past, this approach has been criticized for
a number of failings, including the fact that the order in meaning of a
monad can depend on the order in which the monad transformers are
applied. \Red{cite} The canonical example of this phenomenon is the
composition of the state monad and the error monad: depending on the
ordering of the two monad transformers, state is preserved or thrown away
upon an error.

>>>>

Monads were originally proposed as a method for organizing computational
effects~\cite{Moggi:1991:NCM:116981.116984}.  One of the key questions
of interest was how to modularly build more complex computational
effects out of simpler ones.  One particular approach, the
\emph{incremental
approach}~\cite{Benton00monadsand,Liang95monadtransformers}, utilizes
monad transformers, which add an extra computation feature to a
pre-existing monad.  In the past, this approach has been criticized for
a number of failings, including the fact that the order in meaning of a
monad can depend on the order in which the monad transformers are
applied. The canonical example of this phenomenon is the
composition of the state monad and the error monad: depending on the
ordering of the two monad transformers, state is preserved or thrown away
upon an error.
